Cognitive Principles and Individual Differences \\ in Human Syllogistic Reasoning

### 2019-11-12 paper/paper-v3.tex
Fix typos

Even though the main logical formalism of Classical Logic (CL) has successfully been applied to our scientific reasoning,
various experimental studies have shown that human reasoning systematically deviates 
from conclusions that are valid under CL (cf.~\cite{wason:68,byrne:89}).
% Originally, one of the objectives in the field of AI and logic programming was to formalize human reasoning and commonsense reasoning~\cite{McCarthy59,McCarthy98}. 
% However, the proposed approaches have been strongly critized~(cf.~\cite{mcdermott:87}).
% On the other hand, cognitive scientists have extensively investigated and acquired a great expertise
% in human thinking. Recently, several attempts have been made to bridge the gap among these disciplines. 
% % as they were mostly theoretical and did not apply to real case studies.
% However, only recently an attempt was made 
% this expertise was not consulted, i.e. there was no communication among the relevant fields. 
Cognitive theories that try to explain human reasoning need to be evaluated by their cognitive adequacy~\cite{strube:1992} and their performance should be compared to other theories.
Conceptual cognitive adequacy describes to what extent a system corresponds to human conceptual knowledge, whereas inferential cognitive adequacy indicates whether the reasoning process of a system is structured similarly to the way humans reason~\cite{knauff:rauh:renz:1997}. 
In order to determine the required factors that are necessary for the evaluation of an adequate cognitive theory, we take~the suggestion by Ragni and Stolzburg~\cite{ragni:stolzenburg:2015} as a starting point:
We aim for a theory in which (i) all processes are comprehensible, (ii) the suggested underlying represent general cognitive processes, and (iii) the predictions of our theory are evaluated with respect to a wide range of human reasoning tasks.

@@

Consider the statement \textit{No y is z.} ({\ME yz}):
Similarly to the previous case, \licenses and \import apply here
as well.
The logic programs specified in Subsection~\ref{sect:wcs} 
do not allow heads of clauses to be negative literals. Therefore, a negative conclusion~$\neg p(X)$ is represented
by introducing an auxiliary formula $p'(X)$ together with the clause $p(X) \leftarrow \neg p'(X)$ and the integrity constraint $\udf \leftarrow p(X) \wedge p'(X)$ (\transformation). This is a widely used technique in Logic Programming (e.g. choice rules in~\cite{GebserKaminskiKaufmannSchaub12}). 
Another principle that we introduce is the \emph{no double negation} principle: Under the Weak Completion Semantics, a positive conclusion can be derived from double negation appearing in two conditionals. However, it seems that humans normally do not reason in such a way~\cite{khemlani:2012}. Hence, we block them with the help of abnormalities (\dnegation). $\CalP_{Eyz}$, the logic program representing \ME yz is as follows:
% \footnote{For simplicity, we omitted to list the clauses that are introduced by the (\converse) principle in $\CalP_{Eyz}$: The same clauses just switching $y$ and $z$ are added and thus also the fact $z(o_2) \leftarrow \top$ for another object $o_2$.
% The entire program can be found in~\cite{declare:2017}.}
\begin{align}
 z'(X) & \leftarrow y(X) \wedge \neg \Ab_{ynz}(X).  \tag{\conditionals\ \&\ \transformation\ \&\  \licenses} \\
\Ab_{ynz}(X)  & \leftarrow \cxt(z(X)).\tag{\licenses} \\
z(X) & \leftarrow \neg z'(X) \wedge \neg \Ab_{nzz}(X). \tag{\transformation\ \&\ \licenses} \\
y(o_1) & \leftarrow \top. \tag{\import} \\
\Ab_{nzz}(o_1) & \leftarrow \bot. \tag{\licenses\ \&\  \dnegation}
\end{align}
As we now have both $z(X)$ and $z'(X)$ in the head of some clause, we need to add the 
following integrity constraints: $\udf \leftarrow z(X) \wedge
z'(X)$. We obtain 
\[\CalM_{\CalP_{Eyz}} = \langle \{y(o_1), z'(o_1)\},\{\Ab_{ynz}(o_1), \Ab_{nzz}(o_1),  z(o_1)\}
\rangle.
\]

@@

Consider the statement \textit{Some y are not z} ({\MO yz}), which in CL is represented as $\exists X (y(X) \wedge \neg z(X)$.
As in the previous cases, \conditionals, \licenses and \unknownGen are assumed.
As the conclusion is again a negation of a claim, \transformation and
\dnegation apply as well. $\CalP_{Oyz}$, the logic program representing \MO yz is as follows:
\begin{align}
z'(X) & \leftarrow y(X) \wedge \neg \Ab_{ynz}(X). & \tag{\conditionals\ \&\ \transformation \ \&\ \licenses} \\
\Ab_{ynz}(o_1) & \leftarrow \bot. & \tag{\licenses\ \& \unknownGen} \\
z(X) & \leftarrow  \neg z'(X) \wedge \neg \Ab_{nzz}(X). &
\tag{\licenses\ \&\ \transformation} \\
y(o_1) & \leftarrow \top. & \tag{\import} \\
y(o_2) & \leftarrow \top. & \tag{\unknownGen} \\
\Ab_{nzz}(o_1)& \leftarrow \bot. & \tag{\licenses\ \&\ \dnegation}\\
\Ab_{nzz}(o_2)& \leftarrow \bot. & \tag{\licenses\ \&\ \dnegation}
\end{align}
We have to add the integrity constraint $U \leftarrow z(X) \wedge
z'(X)$
and obtain \[\CalM_{\CalP_{Oyz}} = \langle \{y(o_1), y(o_2), z'(o_1)\},\{\Ab_{ynz}(o_1),
\Ab_{nzz}(o_1), \Ab_{nzz}(o_2), z(o_1) \} \rangle.\]

@@

In FOL, the conditional statement $\forall (X) (a(X) \rightarrow b(X))$, is logically
equivalent to its contrapositive, $\forall (X) (\neg b(X) \rightarrow \neg a(X))$.
% This
% contraposition also holds for the syllogistic moods~\MA\ and~\ME. 
There is
evidence that some of the participants might directly or indirectly 
apply the contrapositive (\contraposition) within a reasoning task (cf.~\cite{rips:1994,mentallogic:1994}).
Consider again $\CalP_{Ayz}$, the logic program representing \MA yz
from Section~\ref{sect:basic}. The clauses that represent the contraposition principles are as follows:
\begin{align}
y'(X) & \leftarrow  \neg z(X) \wedge \neg \Ab_{zy}(X). & \tag{\conditionals\ \&\ \licenses\ \&\ \contraposition\ } \\
\Ab_{zy}(X) & \leftarrow \cxt(y(X)). & \tag{ \licenses\ \&\ \contraposition}\\
y(X) & \leftarrow  \neg y'(X) \wedge \neg \Ab_{nyy}(X). & \tag{\transformation\ \&\ \licenses\ \&\ \contraposition} 
\end{align}
The application of \contraposition for the \ME\ mood,
\textit{No y is z}, yields \textit{No z is y}, and consists of the following clauses:
\begin{align}
y'(X) & \leftarrow z(X) \wedge \neg \Ab_{zny}(X). & \tag{\conditionals\ \&\ \licenses\ \&\ \contraposition\ } \\
\Ab_{zny}(X) & \leftarrow \cxt(y(X)). &\tag{ \licenses\ \&\ \contraposition}\\
y(X) & \leftarrow \neg y'(X) \wedge \neg \Ab_{nyy}(X). & \tag{\transformation\ \&\ \licenses\ \&\ \contraposition} 
% z(o_2) \leftarrow \top. & (\contraposition\  \&\ \import) \\
% \Ab_{nyy}(o_2) \leftarrow \bot. & (\contraposition\  \&\ \licenses\ \&\ \dnegation)
\end{align}

@@

If all principles introduced so far are applied to a pair of existentially quantified premises
(\MI or \MO), then the only object about which an inference can be made is the one
resulting from \import with respect to the premise it introduced (i.e.\ only inferences about the properties 
of the object about $a$ and $b$ or
$b$ and $c$). 
% This is because the
% abnormality (\licenses) and according to (\unknownGen)
%  has to be false only for the object introduced by (\import), but unknown
% for other objects.
There is, however, evidence that some humans still draw conclusions about $a$ and $c$ in such
circumstances, i.e.\ they seem to generalize (universally quantify) the existential 
premise with respect to other objects (\negFailure).
Consider again $\CalP_{I yz}$ of Section~\ref{sect:basic}, where $\Ab_{yz}$ is only false for 
$o_1$. In case \negFailure applies, then $\Ab_{yz}(o_1) \leftarrow \bot$
in $\CalP_{I yz}$ is replaced by the following two clauses:
\begin{align}
\Ab_{yz}(X) & \leftarrow \cxt(z'(X)). & \tag{\licenses\ \&\ \negFailure} \\
\Ab_{yz}(o_2) & \leftarrow \udf. & \tag{\licenses\ \&\ \negFailure} 
\end{align}
Similar to the case of $\CalP_{Ayz}$ for the representation of the basic principles of \MA yz,
the $\cxt$ operator in the body of the first clause is false for all $o$
for which $z'(o)$ is unknown. This clause transforms the representation for the existential quantification over \MI yz in $\CalP_{Iyz}$
into a universal one. In order to maintain \unknownGen, the second clause is added:
$\Ab_{yz}(o_2) \leftarrow \udf$ guarantees that $\Ab_{yz}(o_2)$ stays unknown, even though $\cxt(z'(o_2))$ might be false.
Recall that programs are considered under their weak completion, i.e.\ if $\cxt(z'(o_2))$ is false, then
\[\Ab_{yz}(o_2) \leftrightarrow (\cxt(z'(o_2)) \vee \udf)
 \equiv \Ab_{yz}(o_2) \leftrightarrow \udf.\]
%  is semantically equivalent to $\Ab_{yz}(o_2) \leftrightarrow \udf$ if $\cxt(z'(o_2))$ is false.}

@@

We specify when $\MP$ entails a conclusion with respect to $yz$:\footnote{$yz$ can be replaced by $ac$ or~$ca$.}
\begin{description}
\item[\MA yz (all)] $\CalP \models Ayz$ iff there exists an object $o$ such that $\CalP \ModelsWCS
y(o)$ and for all objects $o$ we find that if $\CalP \ModelsWCS y(o)$ then $\CalP \ModelsWCS z(o)$.
\item [\ME yz (no)]
$\CalP \models Eyz$ iff there exists an object $o_1$ such that $\CalP \ModelsWCS
y(o_1)$ and for all objects $o_1$ we find that if $\CalP \ModelsWCS y(o_1)$ then
$\CalP \ModelsWCS \neg z(o_1)$.\footnote{
When the contraposition principles applies, then additionally 
the following condition needs to hold as well: There exists an object $o_2$ such that $\CalP \ModelsWCS
z(o_2)$ and for all objects $o_2$ we find that if $\CalP \ModelsWCS z(o_2)$ then
$\CalP \ModelsWCS \neg y(o_2)$.}
\item[\MI yz (some)]
$\CalP \models Iyz$ iff there exists an object $o_1$ such that $\CalP \ModelsWCS
y(o_1) \wedge z(o_1)$ and there exists an
object $o_2$ such that $\CalP \ModelsWCS y(o_2)$ and
$\CalP \not\ModelsWCS z(o_2)$ and
% there exists an object $o_3$ such that $\CalP \ModelsWCS
% z(o_3) \wedge y(o_3)$ and 
there exists an
object $o_3$ such that $\CalP \ModelsWCS z(o_3)$ and
$\CalP \not\ModelsWCS y(o_3)$.
\item[\MO yz (some are not)]
$\CalP \models Oyz$ iff there exists an object $o_1$ such that $\CalP \ModelsWCS
y(o_1) \wedge \neg z(o_1)$ and there exists an
object $o_2$ such that $\CalP \ModelsWCS y(o_2)$ and
$\CalP \not\ModelsWCS \neg z(o_2)$.
\item[\NVC\ (no valid conclusion)] iff none of the previous conclusions can be derived.
\end{description}
For \MI yz (some) the conversion is explicitly specified, motivated by the \converse principle.
By requiring for \MI yz (\MO yz, resp.) the existence of an object with the first property $y$,
for which the second property $z$ has to be either either false or unknown (true or unknown, resp.),
\MA yz and \MI yz, (\ME yz and \MO yz, resp.), exclude each other.

@@

We identified three different clusters: 
The last two columns show the classification of the participants as deliberative, intuitive or intermediate. 
% The participants in the deliberative cluster here corresponds exactly to~\cite{khemlani:2016}. 
Our classification only differs wrt Johnson-Laird and Khemlani's 
classification~\cite{khemlani:2016} for the intermediate and intuitive cluster with respect to three participants (1, 11 and 19).
A possible explanation for this difference, could be that they
did not take into account the participants' changes between week 1 and week 2.

@@

We have investigated the cognitive adequacy of clustering by principles under WCS with respect to the individual answer patterns reported by Johnson-Laird and Khemlanid~\cite{khemlani:2016}.
Their approach is the only one we are aware of that has evaluated predictions on human syllogistic reasoning
with respect to the non-aggregated data.
However in contrast to here, they did not distinguish between the participants' responses in week 1 and week 2.

>>>>

Even though the main logical formalism of Classical Logic (CL) has successfully been applied to our scientific reasoning,
various experimental studies have shown that human reasoning systematically deviates 
from conclusions that are valid under CL (cf.~\cite{wason:68,byrne:89}).
% Originally, one of the objectives in the field of AI and logic programming was to formalize human reasoning and commonsense reasoning~\cite{McCarthy59,McCarthy98}. 
% However, the proposed approaches have been strongly critized~(cf.~\cite{mcdermott:87}).
% On the other hand, cognitive scientists have extensively investigated and acquired a great expertise
% in human thinking. Recently, several attempts have been made to bridge the gap among these disciplines. 
% % as they were mostly theoretical and did not apply to real case studies.
% However, only recently an attempt was made 
% this expertise was not consulted, i.e. there was no communication among the relevant fields. 
Cognitive theories that try to explain human reasoning need to be evaluated by their cognitive adequacy~\cite{strube:1992} and their performance should be compared to other theories.
Conceptual cognitive adequacy describes to what extent a system corresponds to human conceptual knowledge, whereas inferential cognitive adequacy indicates whether the reasoning process of a system is structured similarly to the way humans reason~\cite{knauff:rauh:renz:1997}. 
In order to determine the required factors that are necessary for the evaluation of an adequate cognitive theory, we take~the suggestion by Ragni and Stolzenburg~\cite{ragni:stolzenburg:2015} as a starting point:
We aim for a theory in which (i) all processes are comprehensible, (ii) the suggested underlying represent general cognitive processes, and (iii) the predictions of our theory are evaluated with respect to a wide range of human reasoning tasks.

@@

Consider the statement \textit{No y is z.} ({\ME yz}):
Similarly to the previous case, \licenses\ and \import\ apply here
as well.
The logic programs specified in Subsection~\ref{sect:wcs} 
do not allow heads of clauses to be negative literals. Therefore, a negative conclusion~$\neg p(X)$ is represented
by introducing an auxiliary formula $p'(X)$ together with the clause $p(X) \leftarrow \neg p'(X)$ and the integrity constraint $\udf \leftarrow p(X) \wedge p'(X)$ (\transformation). This is a widely used technique in Logic Programming (e.g. choice rules in~\cite{GebserKaminskiKaufmannSchaub12}). 
Another principle that we introduce is the \emph{no double negation} principle: Under the Weak Completion Semantics, a positive conclusion can be derived from double negation appearing in two conditionals. However, it seems that humans normally do not reason in such a way~\cite{khemlani:2012}. Hence, we block them with the help of abnormalities (\dnegation). $\CalP_{Eyz}$, the logic program representing \ME yz is as follows:
% \footnote{For simplicity, we omitted to list the clauses that are introduced by the (\converse) principle in $\CalP_{Eyz}$: The same clauses just switching $y$ and $z$ are added and thus also the fact $z(o_2) \leftarrow \top$ for another object $o_2$.
% The entire program can be found in~\cite{declare:2017}.}
\begin{align}
 z'(X) & \leftarrow y(X) \wedge \neg \Ab_{ynz}(X).  \tag{\conditionals\ \&\ \transformation\ \&\  \licenses} \\
\Ab_{ynz}(X)  & \leftarrow \cxt(z(X)).\tag{\licenses} \\
z(X) & \leftarrow \neg z'(X) \wedge \neg \Ab_{nzz}(X). \tag{\transformation\ \&\ \licenses} \\
y(o_1) & \leftarrow \top. \tag{\import} \\
\Ab_{nzz}(o_1) & \leftarrow \bot. \tag{\licenses\ \&\  \dnegation}
\end{align}
As we now have both $z(X)$ and $z'(X)$ in the head of some clause, we need to add the 
following integrity constraints: $\udf \leftarrow z(X) \wedge
z'(X)$. We obtain 
\[\CalM_{\CalP_{Eyz}} = \langle \{y(o_1), z'(o_1)\},\{\Ab_{ynz}(o_1), \Ab_{nzz}(o_1),  z(o_1)\}
\rangle.
\]

@@

Consider the statement \textit{Some y are not z} ({\MO yz}), which in CL is represented as $\exists X (y(X) \wedge \neg z(X)$.
As in the previous cases, \conditionals, \licenses, and \unknownGen are assumed.
As the conclusion is again a negation of a claim, \transformation\ and
\dnegation\ apply as well. $\CalP_{Oyz}$, the logic program representing \MO yz is as follows:
\begin{align}
z'(X) & \leftarrow y(X) \wedge \neg \Ab_{ynz}(X). & \tag{\conditionals\ \&\ \transformation \ \&\ \licenses} \\
\Ab_{ynz}(o_1) & \leftarrow \bot. & \tag{\licenses\ \& \unknownGen} \\
z(X) & \leftarrow  \neg z'(X) \wedge \neg \Ab_{nzz}(X). &
\tag{\licenses\ \&\ \transformation} \\
y(o_1) & \leftarrow \top. & \tag{\import} \\
y(o_2) & \leftarrow \top. & \tag{\unknownGen} \\
\Ab_{nzz}(o_1)& \leftarrow \bot. & \tag{\licenses\ \&\ \dnegation}\\
\Ab_{nzz}(o_2)& \leftarrow \bot. & \tag{\licenses\ \&\ \dnegation}
\end{align}
We have to add the integrity constraint $U \leftarrow z(X) \wedge
z'(X)$
and obtain \[\CalM_{\CalP_{Oyz}} = \langle \{y(o_1), y(o_2), z'(o_1)\},\{\Ab_{ynz}(o_1),
\Ab_{nzz}(o_1), \Ab_{nzz}(o_2), z(o_1) \} \rangle.\]

@@

In FOL, the conditional statement $\forall (X) (a(X) \rightarrow b(X))$, is logically
equivalent to its contrapositive, $\forall (X) (\neg b(X) \rightarrow \neg a(X))$.
% This
% contraposition also holds for the syllogistic moods~\MA\ and~\ME. 
There is
evidence that some of the participants might directly or indirectly 
apply the contrapositive (\contraposition) within a reasoning task (cf.~\cite{rips:1994,mentallogic:1994}).
Consider again $\CalP_{Ayz}$, the logic program representing \MA yz
from Section~\ref{sect:basic}. The clauses that represent the contraposition principles are as follows:
\begin{align}
y'(X) & \leftarrow  \neg z(X) \wedge \neg \Ab_{zy}(X). & \tag{\conditionals\ \&\ \licenses\ \&\ \contraposition\ } \\
\Ab_{zy}(X) & \leftarrow \cxt(y(X)). & \tag{ \licenses\ \&\ \contraposition}\\
y(X) & \leftarrow  \neg y'(X) \wedge \neg \Ab_{nyy}(X). & \tag{\transformation\ \&\ \licenses\ \&\ \contraposition} 
\end{align}
The application of \contraposition\ for the \ME\ mood,
\textit{No y is z}, yields \textit{No z is y}, and consists of the following clauses:
\begin{align}
y'(X) & \leftarrow z(X) \wedge \neg \Ab_{zny}(X). & \tag{\conditionals\ \&\ \licenses\ \&\ \contraposition\ } \\
\Ab_{zny}(X) & \leftarrow \cxt(y(X)). &\tag{ \licenses\ \&\ \contraposition}\\
y(X) & \leftarrow \neg y'(X) \wedge \neg \Ab_{nyy}(X). & \tag{\transformation\ \&\ \licenses\ \&\ \contraposition} 
% z(o_2) \leftarrow \top. & (\contraposition\  \&\ \import) \\
% \Ab_{nyy}(o_2) \leftarrow \bot. & (\contraposition\  \&\ \licenses\ \&\ \dnegation)
\end{align}

@@

If all principles introduced so far are applied to a pair of existentially quantified premises
(\MI or \MO), then the only object about which an inference can be made is the one
resulting from \import\ with respect to the premise it introduced (i.e.\ only inferences about the properties 
of the object about $a$ and $b$ or
$b$ and $c$). 
% This is because the
% abnormality (\licenses) and according to (\unknownGen)
%  has to be false only for the object introduced by (\import), but unknown
% for other objects.
There is, however, evidence that some humans still draw conclusions about $a$ and $c$ in such
circumstances, i.e.\ they seem to generalize (universally quantify) the existential 
premise with respect to other objects (\negFailure).
Consider again $\CalP_{I yz}$ of Section~\ref{sect:basic}, where $\Ab_{yz}$ is only false for 
$o_1$. In case \negFailure\ applies, then $\Ab_{yz}(o_1) \leftarrow \bot$
in $\CalP_{I yz}$ is replaced by the following two clauses:
\begin{align}
\Ab_{yz}(X) & \leftarrow \cxt(z'(X)). & \tag{\licenses\ \&\ \negFailure} \\
\Ab_{yz}(o_2) & \leftarrow \udf. & \tag{\licenses\ \&\ \negFailure} 
\end{align}
Similar to the case of $\CalP_{Ayz}$ for the representation of the basic principles of \MA yz,
the $\cxt$ operator in the body of the first clause is false for all $o$
for which $z'(o)$ is unknown. This clause transforms the representation for the existential quantification over \MI yz in $\CalP_{Iyz}$
into a universal one. In order to maintain \unknownGen, the second clause is added:
$\Ab_{yz}(o_2) \leftarrow \udf$ guarantees that $\Ab_{yz}(o_2)$ stays unknown, even though $\cxt(z'(o_2))$ might be false.
Recall that programs are considered under their weak completion, i.e.\ if $\cxt(z'(o_2))$ is false, then
\[\Ab_{yz}(o_2) \leftrightarrow (\cxt(z'(o_2)) \vee \udf)
 \equiv \Ab_{yz}(o_2) \leftrightarrow \udf.\]
%  is semantically equivalent to $\Ab_{yz}(o_2) \leftrightarrow \udf$ if $\cxt(z'(o_2))$ is false.}

@@

We specify when $\MP$ entails a conclusion with respect to $yz$:\footnote{$yz$ can be replaced by $ac$ or~$ca$.}
\begin{description}
\item[\MA yz (all)] $\CalP \models Ayz$ iff there exists an object $o$ such that $\CalP \ModelsWCS
y(o)$ and for all objects $o$ we find that if $\CalP \ModelsWCS y(o)$ then $\CalP \ModelsWCS z(o)$.
\item [\ME yz (no)]
$\CalP \models Eyz$ iff there exists an object $o_1$ such that $\CalP \ModelsWCS
y(o_1)$ and for all objects $o_1$ we find that if $\CalP \ModelsWCS y(o_1)$ then
$\CalP \ModelsWCS \neg z(o_1)$.\footnote{
When the contraposition principles applies, then additionally 
the following condition needs to hold as well: There exists an object $o_2$ such that $\CalP \ModelsWCS
z(o_2)$ and for all objects $o_2$ we find that if $\CalP \ModelsWCS z(o_2)$ then
$\CalP \ModelsWCS \neg y(o_2)$.}
\item[\MI yz (some)]
$\CalP \models Iyz$ iff there exists an object $o_1$ such that $\CalP \ModelsWCS
y(o_1) \wedge z(o_1)$ and there exists an
object $o_2$ such that $\CalP \ModelsWCS y(o_2)$ and
$\CalP \not\ModelsWCS z(o_2)$ and
% there exists an object $o_3$ such that $\CalP \ModelsWCS
% z(o_3) \wedge y(o_3)$ and 
there exists an
object $o_3$ such that $\CalP \ModelsWCS z(o_3)$ and
$\CalP \not\ModelsWCS y(o_3)$.
\item[\MO yz (some are not)]
$\CalP \models Oyz$ iff there exists an object $o_1$ such that $\CalP \ModelsWCS
y(o_1) \wedge \neg z(o_1)$ and there exists an
object $o_2$ such that $\CalP \ModelsWCS y(o_2)$ and
$\CalP \not\ModelsWCS \neg z(o_2)$.
\item[\NVC\ (no valid conclusion)] iff none of the previous conclusions can be derived.
\end{description}
For \MI yz (some) the conversion is explicitly specified, motivated by the \converse\ principle.
By requiring for \MI yz (\MO yz, resp.) the existence of an object with the first property $y$,
for which the second property $z$ has to be either either false or unknown (true or unknown, resp.),
\MA yz and \MI yz, (\ME yz and \MO yz, resp.), exclude each other.

@@

We identified three different clusters: 
The last two columns show the classification of the participants as deliberative, intuitive or intermediate. 
% The participants in the deliberative cluster here corresponds exactly to~\cite{khemlani:2016}. 
Our classification only differs wrt.\ Johnson-Laird and Khemlani's 
classification~\cite{khemlani:2016} for the intermediate and intuitive cluster with respect to three participants (1, 11 and 19).
A possible explanation for this difference could be that they
did not take into account the participants' changes between week 1 and week 2.

@@

We have investigated the cognitive adequacy of clustering by principles under WCS with respect to the individual answer patterns reported by Johnson-Laird and Khemlani~\cite{khemlani:2016}.
Their approach is the only one we are aware of that has evaluated predictions on human syllogistic reasoning
with respect to the non-aggregated data.
However in contrast to here, they did not distinguish between the participants' responses in week 1 and week 2.
